Vaccination

### 2022-03-17 code/vaccination-indicators.Rmd
code update

# Define specific dates
date1 <- "2021-07-11" # Just before pass sanitaire announcement
date2 <- "2021-08-08" # Just before pass sanitaire comes into force
date3 <- "2021-08-29" # Before back to school
date4 <- "2022-01-02" # Last date of the year
```

@@

```{r}
if(runComputations){
  # Define the combinations of parameters to be tested
  parmsLR <- expand.grid(varPred = names(dat.nocorr)[-1], 
                         thedate = c(date1, date2, date3, date4), 
                         predTransform = "discretize_factor", 
                         vaccAge = "adults", 
                         by.prbs = 0.5, 
                         permutation = FALSE,
                         stringsAsFactors = FALSE)
  # Permutation 
  # Number of repetitions
  nrep <- 1000
  # Base combination of parameters
  tmpparmsPerm <- expand.grid(varPred = "French_nlty", 
                              thedate = c(date1, date2, date3, date4), 
                              predTransform = "discretize_factor", 
                              vaccAge = "adults", 
                              by.prbs = 0.5, 
                              permutation = TRUE,
                              stringsAsFactors = FALSE)
  # Add repeated parameters
  for(i in 1:nrep){
    parmsLR <- rbind(parmsLR, tmpparmsPerm)
  }
  rm(tmpparmsPerm)

@@

@@

```{r}
if(runComputations){
  # Define the combinations of parameters to be tested
  parmsDec <- expand.grid(varPred = names(dat.nocorr)[-1], 
                          thedate = c(date1, date2, date3, date4), 
                          predTransform = "discretize", 
                          vaccAge = "by_age", 
                          by.prbs = 0.1, 
                          permutation = FALSE,
                          stringsAsFactors = FALSE)

  # Permutation
  # Base combination of parameters
  tmpparmsPerm <- expand.grid(varPred = "French_nlty", 
                              thedate = c(date1, date2, date3, date4), 
                              predTransform = "discretize", 
                              vaccAge = "by_age", 
                              by.prbs = 0.1, 
                              permutation = TRUE,
                              stringsAsFactors = FALSE)
  # Add repeated parameters
  for(i in 1:nrep){
    parmsDec <- rbind(parmsDec, tmpparmsPerm)
  }
  rm(tmpparmsPerm)

@@

```{r}
if(runComputations){
  dates <- sort(unique(vacc$date))
  minDate <- "2021-05-01"
  dates <- dates[dates >= minDate]

@@

@@

@@

v <- dat.all[, c("codgeo", "French_nlty")]
vx <- v[which(is.na(v$French_nlty)), ]
vx
v[1, ]
head(v)
tail(v)

>>>>

# Define specific dates
date1 <- "2021-07-11" # Just before pass sanitaire announcement
date2 <- "2021-08-08" # Just before pass sanitaire comes into force
date3 <- "2021-09-05" # One month after pass sanitaire
date4 <- "2021-12-12" # Before pass vaccinal announcement
date5 <- "2022-01-23" # Just before pass vaccinal came into force
date6 <- "2022-02-20" # One month after pass sanitaires

datesAnalysis <- c(date1, date2, date3, date4, date5, date6)

date.SP.announcement <- "2021-07-12"
date.SP.implementation <- "2021-08-09"
date.VP.announcement <- "2021-12-16"
date.VP.implementation <- "2022-01-24"

@@

```{r computationAcrossMedianComparisons}
if(runComputations){
  # Define the combinations of parameters to be tested
  parmsLR <- expand.grid(varPred = names(dat.nocorr)[-1], 
                         thedate = datesAnalysis, 
                         predTransform = "discretize_factor", 
                         vaccAge = "adults", 
                         by.prbs = 0.5, 
                         permutation = FALSE,
                         stringsAsFactors = FALSE)
  # Permutation 
  # Number of repetitions
  nrep <- 1000
  # Base combination of parameters
  tmpparmsPerm <- expand.grid(varPred = "Abstention", 
                              thedate = datesAnalysis, 
                              predTransform = "discretize_factor", 
                              vaccAge = "adults", 
                              by.prbs = 0.5, 
                              permutation = TRUE,
                              stringsAsFactors = FALSE)
  # Add repeated parameters
  for(i in 1:nrep){
    parmsLR <- rbind(parmsLR, tmpparmsPerm)
  }
  rm(tmpparmsPerm)

@@

```{r eval = FALSE}
# Elections
tmpPRE <- outLR[is.element(outLR$typePred, "PRE") & outLR$permutation == FALSE, c("varPred", "thedate", "OR", "OR.abs")]
tmpPRE[order(tmpPRE$OR.abs, decreasing = TRUE), ]
```

@@

```{r computationsByDeciles}
if(runComputations){
  # Define the combinations of parameters to be tested
  parmsDec <- expand.grid(varPred = names(dat.nocorr)[-1], 
                          thedate = datesAnalysis, 
                          predTransform = "discretize", 
                          vaccAge = "by_age", 
                          by.prbs = 0.1, 
                          permutation = FALSE,
                          stringsAsFactors = FALSE)

  # Permutation
  # Base combination of parameters
  tmpparmsPerm <- expand.grid(varPred = "Abstention", 
                              thedate = datesAnalysis, 
                              predTransform = "discretize", 
                              vaccAge = "by_age", 
                              by.prbs = 0.1, 
                              permutation = TRUE,
                              stringsAsFactors = FALSE)
  # Add repeated parameters
  for(i in 1:nrep){
    parmsDec <- rbind(parmsDec, tmpparmsPerm)
  }
  rm(tmpparmsPerm)

@@

```{r computationsOverTime}
if(runComputations){
  dates <- sort(unique(vacc$date))
  minDate <- "2021-05-01"
  dates <- dates[dates >= minDate]

@@

## Indicators

@@

## Vaccination

```{r}
# Choose date
thedate <- date6
# Vaccination data by age at that date
tmpVacc <- vacc[vacc$date == thedate & vacc$classe_age != "TOUT_AGE", ]
#tmpVacc2 <- vacc[vacc$date == thedate & vacc$classe_age == "TOUT_AGE", ]
#tmpVacc2$taux_cumu <- tmpVacc2$taux_cumu_1_inj

# Compute adult vaccination rate
adultVaccinationRate <- adultVacc(tmpVacc)

#plotMapVacc(adultVaccinationRate, thetitle = paste0("Adult vaccination rates on ", thedate), palName = "Hiroshige", byp = 5)

# Compute mean vaccination rate
meanVacc <- sum(adultVaccinationRate$n_cumu) / sum(adultVaccinationRate$population_carto)
# Compute difference to max to center the color scale
maxDiff <- max(c(max(adultVaccinationRate$taux_cumu) - meanVacc, meanVacc - min(adultVaccinationRate$taux_cumu)))

plotMapVacc(adultVaccinationRate, thetitle = paste0("Adult vaccination rates on ", thedate), palName = "Hiroshige", byp = 2, zmin = floor(100*(meanVacc - maxDiff)), zmax = ceiling(100*(meanVacc + maxDiff)))

#plotMapVacc(tmpVacc2, thetitle = paste0("Adult vaccination rates on ", date6))

# Compute values for the paper

```{r}
head(vacc)
## Population size
# Note: DROMs have already been excluded when loading the `vacc` dataset
totPopSize <- sum(vacc[vacc$date == date2 & vacc$classe_age == "TOUT_AGE", "population_carto"])
totPopSize.adults <- sum(vacc[vacc$date == date2 & vacc$classe_age != "TOUT_AGE" & vacc$classe_age != "00-19", "population_carto"])

## Indicators
nIndicatorsTot <- ncol(dat.all[, ])
nIndicatorsAfterRemovingCorrMiss <- ncol(dat.nocorr[, -1])

tmp <- vacc[vacc$date == date1 & vacc$classe_age == "TOUT_AGE", ]
nlocalities <- table(nchar(tmp$codgeo))
names(nlocalities) <- c("PLM", "EPCI")

```{r}
# Population size
computeTotPop <- function(thedate){
  tmp <- vacc[vacc$date == thedate & vacc$classe_age == "TOUT_AGE", ]
  # Make sure to have the localities we want
  sub <- merge(tmp, data.frame(codgeo = dat.all$codgeo), by = "codgeo")
  c(sum(sub$population_carto, na.rm = TRUE), sum(tmp$population_carto, na.rm = TRUE))
}

rm(thedate)
dts <- sort(unique(vacc$date))
pops <- as.data.frame(t(vapply(dts, computeTotPop, FUN.VALUE = c(1, 2))))
names(pops) <- c("totPop.noNALoc", "totPop")
pops
data.frame(date = dts, population = pops)

tmp <- vacc[vacc$codgeo == "75115" & vacc$classe_age == "TOUT_AGE", c("date", "population_carto")]
tmp

tmp <- vacc[vacc$codgeo == "75115" & vacc$classe_age == "20-39", c("date", "population_carto")]
tmp

# Problem: total population size is constant, seems like population size is not updated in the dataset? 
```

```{r}

# Global vaccination rate
computeGlobalVacc <- function(thedate, adults = TRUE){
  if(adults){
      tmp <- vacc[vacc$date == thedate & 
                    vacc$classe_age != "TOUT_AGE" & 
                    vacc$classe_age != "00-19", ]
  }else{
      tmp <- vacc[vacc$date == thedate & vacc$classe_age == "TOUT_AGE", ]
  }
  # Make sure to have the localities we want
  sub <- merge(tmp, data.frame(codgeo = dat.all$codgeo), by = "codgeo")

  # Compute total populations
  totVacc <- sum(sub$effectif_cumu_1_inj, na.rm = TRUE)
  totPop <- sum(sub$population_carto, na.rm = TRUE)
  c(totVacc/totPop, totVacc, totPop)
}

txVaccAdults <- as.data.frame(t(vapply(dts, computeGlobalVacc, FUN.VALUE = c(1, 2, 3))))
txVaccTot <- as.data.frame(t(vapply(dts, computeGlobalVacc, FUN.VALUE = c(1, 2, 3), adults = FALSE)))

names(txVaccAdults) <- names(txVaccTot) <- c("txVacc", "nVacc", "nTot")
txVaccAdults$date <- rownames(txVaccAdults)
txVaccTot$date <- rownames(txVaccTot)

plot(as.Date(txVaccAdults$date), txVaccAdults$txVacc, ylim = c(0, 1), xlim = c(as.Date("2021-05-01"), as.Date("2022-02-01")), type = "l")
```

Compute district size distribution

```{r}
tmp <- vacc[vacc$date == "2022-01-02" & vacc$classe_age == "TOUT_AGE", ]
# Get the ones for which we have data
tmpp <- merge(tmp, data.frame(codgeo = dat.all$codgeo), by = "codgeo")

popSizeDistribMedian <- median(tmpp$population_carto)
popSizeDistribMedian

popSizeDistrib <- quantile(tmpp$population_carto, probs = c(0.25, 0.5, 0.75))
popSizeDistrib["50%"]

```{r}
# max ORs
maxOR.Unemployment_Benef <- outLR[outLR$varPred == "Unemployment_Benef" & outLR$thedate == max(outLR$thedate), "OR.abs"]
```

Export

```{r}
save(totPopSize, totPopSize.adults, 
     nIndicatorsTot, nIndicatorsAfterRemovingCorrMiss, 
     datesAnalysis,
     nlocalities, 
     nrep,
     date.SP.announcement, date.SP.implementation, date.VP.announcement, date.VP.implementation, 
     dicPred, dic.fullpred,
     vacc,
     epci.PLM,
     txVaccAdults, 
     txVaccTot,
     popSizeDistrib, 
     pops, 
     maxOR.Unemployment_Benef,
     file = "savevalues.RData")

@@

v <- dat.all[, c("codgeo", "Abstention")]
vx <- v[which(is.na(v$Abstention)), ]
vx
v[1, ]
head(v)
tail(v)
